---
title: "simulated_example_blfrm"
author: "Bohan Wu"
date: "3/8/2021"
output: html_document
---

```{r}
#install.packages(c("fda", "coda", "truncdist", "mvtnorm", "dplyr","tidyverse"))
#library(devtools)
#install_github('drkowal/dfosr')
```
```{r setup, include=FALSE}
library(dfosr)
library(tidyverse)
source(here::here("source", "BLFRM.R"))

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_minimal() + theme(legend.position = "bottom"))
```

This document includes a brief demonstration of the Bayesian Linear Factor Regression method for simulated data. The data was generated using methods included in the "dfosr" package. 

## Example data

data simulated with "dfosr" package

```{r}
n = 200 # Number of subjects
T = 50  # Number of observation points
p_0 = 10 # Number of true zero regression coefficients
p_1 = 10 # Number of true nonzero regression coefficients

# Simulate and store the output:
sim_data = simulate_dfosr(T = n, m = T, p_0 = p_0, p_1 = p_1)
Y = sim_data$Y; X = sim_data$X ; tau = sim_data$tau;

plot_F(Y)
```
## Fit BLFRM

Next we fit the proposed method using the `BLFRM()` function. 

```{r}
blfrm_results <- BLFRM(X,Y,k= 5,S = 1000)
```

The plot below shows:
1) the curve posterior means with posterior credible intervals (pointwise and joint), the observed data, and true curves 
```{r}
nburn = 5000
```

```{r}
samples = sample(seq(n), 3,replace = TRUE)
plot_F(Y[samples,],alpha = 2,col= TRUE)
```
```{r}
for(s in samples){
plot_fitted(Y[s,], rowMeans(blfrm_results$post_Yhat[s,,-seq(nburn)]), t(blfrm_results$post_Yhat[s,,-seq(nburn)]), y_true = Y[s,], t01 = NULL,
  include_joint_bands = FALSE)
}
```
2)Compute the summary statistics for the effective sample size (ESS) across posterior samples for beta,theta
```{r}
aperm(blfrm_results$post_Theta[,,-seq(nburn)], c(3,2,1))%>%getEffSize()
```
